---
title: "ZhenMeasure Quick Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ZhenMeasure Quick Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

ZhenMeasure provides a modular workflow for pig feeding station data processing,
including data reading, QC, phenotype calculation, and structured outputs.

## 1. Core Entry Point

- `run_zhen_measure()` is the main entry point for the full pipeline.

## 2. Run Modes

- `read_only`: load and standardize records.
- `qc_only`: run Overall/Feed/Weight QC and write QC outputs.
- `full_run`: run QC and phenotype calculation.

## 3. Visualization Parameters

The plotting capability is controlled by two boolean parameters:

- `growth_curve_test = TRUE`: write a combined PDF named `growth_curves.pdf`.
- `growth_curve = TRUE`: write one PDF per animal under `growth_curves/`.

The plot layout is 2x3 panels for each animal:

- Original Age vs Feed Intake
- Original Feed Intake vs Duration
- Original Age vs Weight
- Cleaned Age vs Feed Intake
- Cleaned Feed Intake vs Duration
- Cleaned Age vs Weight

## 4. Minimal Full Run Example

```{r}
library(ZhenMeasure)

res <- run_zhen_measure(
  data_path = "path/to/raw/data",
  data_type = "YANGXIANG",
  format_path = "path/to/data_format.json",
  output_dir = "output/run1",
  growth_curve = TRUE,
  growth_curve_test = TRUE,
  target_weight_stages = "YANGXIANG",
  phenotype_method = "report"
)
```

## 5. Output Files

When `output_dir` is provided, `qc_only` or `full_run` writes:

- `corrected_standard_records.csv`
- `corrected_records.csv`
- `corrected_daily_records.csv`
- `error_type_summary.csv`
- `animal_qc_summary.csv`
- `qc_run_summary.txt`
- `phenotypes.csv` (full run)
- `growth_curves.pdf` (when `growth_curve_test = TRUE`)
- `growth_curves/*.pdf` (when `growth_curve = TRUE`)

## 6. QC Method

Since V1.0.0, only the `national_standard` QC method is supported.
The legacy method has been removed. Optional enhancements include:

- **STL time-series feed anomaly detection** (`use_stl_feed = TRUE`)
- **Gompertz growth curve weight anomaly detection** (`use_gompertz = TRUE`)

Both are disabled by default. See `?run_zhen_measure` for details.
